### 2018-12-11 papers/basic-theory/figures/dipole-block/dipole-block.tex
Hari and Patrick's edits.

\begin{document}
  \begin{tikzpicture}[auto, node distance=2cm,>={Latex[length=2mm]}]
    \tikzset{font={\fontsize{9pt}{12}\selectfont}}
    \node [block, align=center] (sad) {$f(\ro{}, \so)$\\ Dipole\\ density};
    \node [block,  right of=sad, node distance=4cm] (ads) {$F_\ell^m(\ro)$\\ Angular\\ dipole\\ spectrum};
    \node [block,  right of=ads, node distance=9cm] (irr) {$g(\rd)$\\ Scaled\\ irradiance};
    \node [block, below of=ads, node distance=2.5cm] (sas) {$\mathsf{F}_\ell^m(\bs{\nu})$\\ Spatio-angular\\ dipole\\ spectrum};
    \node [block,  right of=sas, node distance=9cm] (is) {$G(\bs{\nu})$\\ Scaled\\ irradiance\\ spectrum};
    \node [block, below of=sad, node distance=2.5cm] (sds) {$F(\bs{\nu}, \so)$\\ Spatial\\ dipole\\ spectrum};
    \draw [->] (sad) -- node[] {$\mathcal{F}_{\mathbb{S}^2}$} (ads);        
    \draw [->] (ads) -- node[left] {$\mathcal{F}_{\mathbb{R}^2}$} (sas);
    \draw [->] (sds) -- node[] {$\mathcal{F}_{\mathbb{S}^2}$} (sas);
    \draw [->] (sad) -- node[left] {$\mathcal{F}_{\mathbb{R}^2}$} (sds);
    \draw [->] (is) -- node[left] {$\mathcal{F}^{-1}_{\mathbb{R}^2}$} (irr);

    \draw [->] (ads) -- node[text width=4cm, align=center] (cap1) {Angular dipole\\ transfer function\\ $\sum_{\ell m}\gray{H_\ell^m(\rd - \ro)}F_\ell^m(\ro)$} (irr);
    \draw [->] (sad.north) -- ++(0,1.0cm) -- node[right=2.cm, above, align=center] {Dipole point\\ spread function\\ $\int_{\mbb{S}^2}d\so\, \int_{\mbb{R}^2} d\ro\, \gray{h(\rd - \ro, \so)}f(\ro, \so)$} ++(13cm,0) --  (irr.north);
    \draw [->] (sds.south) -- ++(0,-1.0cm) -- node[right=1.95cm, above, align=center] {Spatial dipole\\ transfer function\\ $\int_{\mbb{S}^2}d\so\, \gray{H(\bs{\nu}, \so)}F(\bs{\nu}, \so)$} ++(13cm,0) -- (is.south);
    \draw [->] (sas) -- node[text width=4cm, align=center] {Spatio-angular dipole\\ transfer function\\ $\sum_{\ell m}\gray{\mathsf{H}_\ell^m(\bs{\nu})}\mathsf{F}_\ell^m(\bs{\nu})$} (is);

>>>>

\begin{document}
  \begin{tikzpicture}[auto, node distance=2cm,>={Latex[length=2mm]}]
    \tikzset{font={\fontsize{9pt}{12}\selectfont}}
    \node [block, align=center] (sad) {$f(\ro{}, \so)$\\ Dipole\\ density};
    \node [block,  right of=sad, node distance=4cm] (ads) {$F_\ell^m(\ro)$\\ Dipole\\ angular\\ spectrum};
    \node [block,  right of=ads, node distance=9cm] (irr) {$g(\rd)$\\ Scaled\\ irradiance};
    \node [block, below of=ads, node distance=2.5cm] (sas) {$\mathsf{F}_\ell^m(\bs{\nu})$\\ Dipole\\ spatio-angular\\ spectrum};
    \node [block,  right of=sas, node distance=9cm] (is) {$G(\bs{\nu})$\\ Scaled\\ irradiance\\ spectrum};
    \node [block, below of=sad, node distance=2.5cm] (sds) {$F(\bs{\nu}, \so)$\\ Dipole\\ spatial\\ spectrum};
    \draw [->] (sad) -- node[] {$\mathcal{F}_{\mathbb{S}^2}$} (ads);        
    \draw [->] (ads) -- node[left] {$\mathcal{F}_{\mathbb{R}^2}$} (sas);
    \draw [->] (sds) -- node[] {$\mathcal{F}_{\mathbb{S}^2}$} (sas);
    \draw [->] (sad) -- node[left] {$\mathcal{F}_{\mathbb{R}^2}$} (sds);
    \draw [->] (is) -- node[left] {$\mathcal{F}^{-1}_{\mathbb{R}^2}$} (irr);

    \draw [->] (ads) -- node[text width=4cm, align=center] (cap1) {Dipole angular\\ transfer function\\ $\sum_{\ell m}\int_{\mbb{R}^2}d\ro \gray{H_\ell^m(\rd - \ro)}F_\ell^m(\ro)$} (irr);
    \draw [->] (sad.north) -- ++(0,1.0cm) -- node[right=2.cm, above, align=center] {Dipole point\\ spread function\\ $\int_{\mbb{S}^2}d\so\, \int_{\mbb{R}^2} d\ro\, \gray{h(\rd - \ro, \so)}f(\ro, \so)$} ++(13cm,0) --  (irr.north);
    \draw [->] (sds.south) -- ++(0,-1.0cm) -- node[right=1.95cm, above, align=center] {Dipole spatial\\ transfer function\\ $\int_{\mbb{S}^2}d\so\, \gray{H(\bs{\nu}, \so)}F(\bs{\nu}, \so)$} ++(13cm,0) -- (is.south);
    \draw [->] (sas) -- node[text width=4cm, align=center] {Dipole spatio-angular\\ transfer function\\ $\sum_{\ell m}\gray{\mathsf{H}_\ell^m(\bs{\nu})}\mathsf{F}_\ell^m(\bs{\nu})$} (is);

### 2018-12-11 papers/basic-theory/figures/transfer-functions/transfer-functions.tex
Hari and Patrick's edits.

% Talon's custom commands
\newcommand{\argmin}{\arg\!\min}
\newcommand{\me}{\mathrm{e}}
\providecommand{\e}[1]{\ensuremath{\times 10^{#1}}} 
\providecommand{\mb}[1]{\mathbf{#1}}
\providecommand{\mf}[1]{\mathfrak{#1}}
\providecommand{\mc}[1]{\mathcal{#1}}
\providecommand{\ro}{\mathbf{\mathbf{r}}_o}
\providecommand{\so}{\mathbf{\hat{s}}_o}
\providecommand{\rp}{\mathbf{r}_p}
\providecommand{\rbm}[1]{r_b^{\text{m}}}
\providecommand{\rd}{\mathbf{r}_d}
\providecommand{\rdf}{\mathpzc{r}_d}
\providecommand{\mh}[1]{\mathbf{\hat{#1}}}
\providecommand{\mbb}[1]{\mathbb{#1}}
\providecommand{\bs}[1]{\boldsymbol{#1}}
\providecommand{\bv}{\bs{\nu}}
\providecommand{\bvp}{\bs{\nu}_p}
\providecommand{\bsh}[1]{\hat{\boldsymbol{#1}}}
\providecommand{\nan}{\left(\frac{\text{NA}}{n_o}\right)}
\providecommand{\lmsum}{\sum_{l=0}^\infty\sum_{m=-l}^{l}}
\providecommand{\intr}[1]{\int_{\mbb{R}^{#1}}}
\providecommand{\ints}[1]{\int_{\mbb{S}^{#1}}}
\DeclareFontFamily{OT1}{pzc}{}
\DeclareFontShape{OT1}{pzc}{m}{it}{<-> s * [1.10] pzcmi7t}{}
\DeclareMathAlphabet{\mathpzc}{OT1}{pzc}{m}{it}
\newcommand{\eqname}[1]{\tag*{#1}}
\newcommand*\widefbox[1]{\fbox{\hspace{1em}#1\hspace{1em}}}

\tikzstyle{block} = [draw, fill=white, rectangle, minimum height=4em, minimum width=10em, align=center]
\begin{document}
  \begin{tikzpicture}[auto, node distance=2.5cm,>={Latex[length=2mm]}]
    \tikzset{font={\fontsize{9pt}{12}\selectfont}}
    \node [block, align=center] (sad) {$h(\rd - \ro, \so)$\\ Dipole point\\ spread function};
    \node [block,  right of=sad, node distance=5.5cm] (ads) {$H_\ell^m(\rd - \ro)$\\ Angular dipole\\ transfer function};
    \node [block,  left of=sad, node distance=5.5cm] (e) {$\mb{c}(\rd - \ro, \so)$\\ Coherent dipole \\ spread function};
      \node [block, below of=ads, node distance=2.5cm] (sas) {$\mathsf{H}_\ell^m(\bs{\nu})$\\ Spatio-angular\\ dipole transfer function};
      \node [block, below of=sad, node distance=2.5cm] (sds) {$H(\bs{\nu}, \so)$\\ Dipole\\ transfer function};
        \node [block,  left of=sds, node distance=5.5cm] (e2) {$\mb{C}(\bvp,\so)$\\ Coherent dipole \\transfer function};
      \draw [->] (sad) -- node[shift={(0,0)}] {$\mathcal{F}_{\mathbb{S}^2}$} (ads);
      \draw [->] (e) -- node[shift={(0,.75)}] {$|\mb{c}(\rd - \ro, \so)|^2$} (sad);
      % \draw [->] (e2) -- node[] {$\int_{\mbb{R}^2}d\rb \mb{E}_{\text{bfp}}(\rb, \so)\mb{E}_{\text{bfp}}^\dagger(\rb - \bs{\nu}, \so)$} (sds);
            \draw [->] (e2) -- node[below, shift={(0,-0.75)}] {$\int_{\mbb{R}^2}d\bvp\, \mb{C}(\bvp, \so)\mb{C}^\dagger(\bvp - \bs{\nu}, \so)$} (sds);        
      \draw [->] (ads) -- node[left, shift={(0,0)}] {$\mathcal{F}_{\mathbb{R}^2}$} (sas);
          \draw [->] (e) -- node[left] {$\mathcal{F}_{\mathbb{R}^2}$} (e2);
    \draw [->] (sds) -- node[below, shift={(0,0)}] {$\mathcal{F}_{\mathbb{S}^2}$} (sas);
    \draw [->] (sad) -- node[left] {$\mathcal{F}_{\mathbb{R}^2}$} (sds);
      \end{tikzpicture}
\end{document}

>>>>

% Talon's custom commands
\newcommand{\argmin}{\arg\!\min}
\newcommand{\me}{\mathrm{e}}
\providecommand{\e}[1]{\ensuremath{\times 10^{#1}}} 
\providecommand{\mb}[1]{\mathbf{#1}}
\providecommand{\mf}[1]{\mathfrak{#1}}
\providecommand{\mc}[1]{\mathcal{#1}}
\providecommand{\ro}{\mathbf{\mathbf{r}}_o}
\providecommand{\so}{\mathbf{\hat{s}}_o}
\providecommand{\rp}{\mathbf{r}_p}
\providecommand{\rbm}[1]{r_b^{\text{m}}}
\providecommand{\rd}{\mathbf{r}_d}
\providecommand{\rdf}{\mathpzc{r}_d}
\providecommand{\mh}[1]{\mathbf{\hat{#1}}}
\providecommand{\mbb}[1]{\mathbb{#1}}
\providecommand{\bs}[1]{\boldsymbol{#1}}
\providecommand{\bv}{\bs{\nu}}
\providecommand{\bvp}{\bs{\tau}}
\providecommand{\bsh}[1]{\hat{\boldsymbol{#1}}}
\providecommand{\nan}{\left(\frac{\text{NA}}{n_o}\right)}
\providecommand{\lmsum}{\sum_{l=0}^\infty\sum_{m=-l}^{l}}
\providecommand{\intr}[1]{\int_{\mbb{R}^{#1}}}
\providecommand{\ints}[1]{\int_{\mbb{S}^{#1}}}
\DeclareFontFamily{OT1}{pzc}{}
\DeclareFontShape{OT1}{pzc}{m}{it}{<-> s * [1.10] pzcmi7t}{}
\DeclareMathAlphabet{\mathpzc}{OT1}{pzc}{m}{it}
\newcommand{\eqname}[1]{\tag*{#1}}
\newcommand*\widefbox[1]{\fbox{\hspace{1em}#1\hspace{1em}}}

\tikzstyle{block} = [draw, fill=white, rectangle, minimum height=4em, minimum width=10em, align=center]
\begin{document}
  \begin{tikzpicture}[auto, node distance=2.5cm,>={Latex[length=2mm]}]
    \tikzset{font={\fontsize{9pt}{12}\selectfont}}
    \node [block, align=center] (sad) {$h(\rd - \ro, \so)$\\ Dipole point\\ spread function};
    \node [block,  right of=sad, node distance=5.5cm] (ads) {$H_\ell^m(\rd - \ro)$\\ Dipole angular\\ transfer function};
    \node [block,  left of=sad, node distance=5.5cm] (e) {$\mb{c}(\rd - \ro, \so)$\\ Dipole coherent \\ spread function};
      \node [block, below of=ads, node distance=2.5cm] (sas) {$\mathsf{H}_\ell^m(\bs{\nu})$\\ Dipole spatio-angular\\ transfer function};
      \node [block, below of=sad, node distance=2.5cm] (sds) {$H(\bs{\nu}, \so)$\\ Dipole spatial\\ transfer function};
        \node [block,  left of=sds, node distance=5.5cm] (e2) {$\mb{C}(\bvp,\so)$\\ Dipole coherent \\transfer function};
      \draw [->] (sad) -- node[shift={(0,0)}] {$\mathcal{F}_{\mathbb{S}^2}$} (ads);
      \draw [->] (e) -- node[shift={(0,.75)}] {$|\mb{c}(\rd - \ro, \so)|^2$} (sad);
      % \draw [->] (e2) -- node[] {$\int_{\mbb{R}^2}d\rb \mb{E}_{\text{bfp}}(\rb, \so)\mb{E}_{\text{bfp}}^\dagger(\rb - \bs{\nu}, \so)$} (sds);
            \draw [->] (e2) -- node[below, shift={(0,-0.75)}] {$\int_{\mbb{R}^2}d\bvp\, \mb{C}(\bvp, \so)\mb{C}^\dagger(\bvp - \bs{\nu}, \so)$} (sds);        
      \draw [->] (ads) -- node[left, shift={(0,0)}] {$\mathcal{F}_{\mathbb{R}^2}$} (sas);
          \draw [->] (e) -- node[left] {$\mathcal{F}_{\mathbb{R}^2}$} (e2);
    \draw [->] (sds) -- node[below, shift={(0,0)}] {$\mathcal{F}_{\mathbb{S}^2}$} (sas);
    \draw [->] (sad) -- node[left] {$\mathcal{F}_{\mathbb{R}^2}$} (sds);
      \end{tikzpicture}
\end{document}
